### 2016-01-15 paper.tex
Max on C_P is a subscript rather than separated by comma

For example, the effect of Reynolds number on average power output was shown to
be significant on the 2 m Sandia Research Darrieus turbine in wind tunnel
testing \cite{Blackwell1976}: Maximum power coefficient, $C_{P,\mathrm{max}}$,
increased with Reynolds number, $Re_c$, along with a shift of the location of
$C_{P,\mathrm{max}}$ toward lower tip speed ratios due to delayed blade stall.
The effects of Reynolds number were quite dramatic over a relatively small range
of $Re_c \approx 1.1 \times 10^5$--$2.9 \times 10^5$. More recently, Bachant and
Wosnik \cite{Bachant2014, Bachant2015-RVAT-Re-dep} showed that turbine
performance and near-wake characteristics become Reynolds number independent at
$Re_c \approx 2 \times 10^5$.

>>>>

For example, the effect of Reynolds number on average power output was shown to
be significant on the 2 m Sandia Research Darrieus turbine in wind tunnel
testing \cite{Blackwell1976}: Maximum power coefficient, $C_{P_{\max}}$,
increased with Reynolds number, $Re_c$, along with a shift of the location of
$C_{P_{\max}}$ toward lower tip speed ratios due to delayed blade stall. The
effects of Reynolds number were quite dramatic over a relatively small range of
$Re_c \approx 1.1 \times 10^5$--$2.9 \times 10^5$. More recently, Bachant and
Wosnik \cite{Bachant2014, Bachant2015-RVAT-Re-dep} showed that turbine
performance and near-wake characteristics become Reynolds number independent at
$Re_c \approx 2 \times 10^5$.
